Size, Shape and Functionality Dependence of Solute Transport Mechanisms in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-02-05 Ben_Manuscripts/transport/Outline.tex
Outline updates

  \subsection{Governing Mechanisms}\label{section:mechanism_overview}

@@

  % BJC: would it be better to report as a fraction of water MSD?
  \noindent We calculated the time-averaged MSD of each solute in the set over the
  course of 1 $\mu$s MD simulations. 
  \begin{itemize}
    \item Because the MSDs are non-linear and because of the ageing phenomenon, we
    did not attempt to calculate a diffusion constant as one might for a Brownian
    particle with a linear MSD.
	\item Instead, the values plotted in Figure~\ref{fig:all_msds} represent the
	average MSD of each solute after a 400 ns time lag.
  \end{itemize}

@@

  \noindent The MSDs in Figure~\ref{fig:all_msds} are a strong function of two solute 
  trapping mechanisms. % by which solutes become trapped.
  \begin{itemize}
  	\item Solutes that are hydrogen bond donors can be stabilized through hydrogen bonds
  	with one of the five oxygen atoms attached to each monomer head group. 
  	\item In a separate interaction, solutes can become kinetically trapped between 
  	monomer head groups.
  	\item Generally, both mechanisms affect each solute to varying degrees.
  \end{itemize}

@@

  \noindent A solute's size, shape, and polarity dictate the degree to which they 
  are influenced by each entrapment mechanism.
  \begin{itemize}
    \item In general, solutes can move fastest in the pore center, where
    there is comparatively little resistance to diffusion.
%    \item The smallest molecular weight solutes move fastest.
    \item Low molecular weight, highly water-soluble, hydrogen bond donating molecules spend the most time
    in the pore center where they are slowed down primarily by hydrogen bonds
    with monomer carboxylate groups.
    %BJC: this isn't fully accurate yet. Need to come back to this
    \item Solutes that cannot donate hydrogen bonds, or are less miscible in water, 
    tend to partition into the head group region where entrapment occurs. Most of
    the anti-correlated motion occurs here.
    \item The inverse relationship between solute size and mobility is disrupted
    by solutes' preference for water. 
    \item We observe low MW solutes with lower-than-expected MSDs because they
    spend more time trapped between monomer head groups due to low water
    solubility.
    \item Small, planar molecules exhibit some of the shortest MSDs because

  	\item The well-established trend of decreasing solute mobility with 
  	size is not defied here, however 
  	\item Additionally, planar molecules are prone to exhibiting similar
  	trapping behavior, even for large molecules whose similar sized, but flexible
  	counterparts exhibit faster diffusion.  %BJC: this is unproven
  	\item The polarity of solutes also influences a solute's ability to stay in
  	the pore center. Highly polar molecules tend to spend more time in the pore center,
  	while those with hydrophobic character tend to spend more time in the head group
  	region.
  	\item Finally, the ability to hydrogen bond offers a second trapping mechanism. 
  	Solutes that are hydrogen bond donors can donate hydrogen atoms to
  	any of the 5 oxygen atoms located on the monomer head groups. Increasing the 
  	number of hydrogen bond donating groups increases the solute's polarity causing
  	solutes to spend more time in the pore centers, but the effect can be countered
  	by excessive trapping if there are many hydrogen bonds being formed.
  	\item Overall solutes exhibit some degree of trapping, by one or a combination of the above
  	mechanisms, with anticorrelated hops between each period of immobility due to 
  	obstructions.
  \end{itemize}

@@

  \subsection{Mean Squared Displacement Predictions}\label{section:msd_predictions}

  %BJC: focus on MD MSD results

  \subsubsection*{The Influence of Water Content on Macroscopic Diffusion Coefficients}

  Solutes in systems with lower water content exhibit lower diffusion coefficients.
  \begin{itemize}
	\item Pores are more crowded when there is less water (show RDFs of each)
	\item Not a linear function of pore size - radius increase by x, D increases by y
	\item Larger influence on bigger molecules
  \end{itemize}

  \subsubsection{Experimental Measurements}

  % For Greg

  \subsection{Transport Mechanisms}

  In order to truly understand the molecular origins of the macroscopic
  diffusion coefficients in Section~\ref{section:D_macro}, we studied the
  microscopic interactions between solutes and the membrane that lead to the
  observed dwell time and hop distributions.
  \begin{itemize}
	\item We studied the radial distribution functions of solutes as a
	function of distance from the pore center
	\item We looked at hydrogen bonding patterns
	\item Coordination numbers
	\item Order parameters
  \end{itemize}

  The radial distribution function of each solute studied is shown in 
  Figure TBD.

  \subsubsection*{Transport of Water}

  All water molecules exhibit hop diffusion.

@@

  \subsubsection*{Transport of Alcohols}

  The hydroxyl functional group of alcohol molecules is a hydrogen bond donor
  and prefers to donate it's hydrogen to more strongly polarized carboxylate head
  groups.

  As alcohol groups increase in hydrophobic character, they are more inclined
  to stick to the outside edges of the pore. 
  \begin{itemize}
	\item The alkane tails prefer to stay at the edges of the pore.
	\item Radial distribution functions show peaks at pore edges, however
	smaller alcohols have high densities near the pore center. 
	\item They tend to get trapped between monomers and closer to 
	the tail region. 
	\item The entrapment is further stabilized by hydrogen bonds with
	ether oxygens connecting the monomer's alkane tails to the head groups.
	%TODO: quantify h-bonds with ether oxygens and carbonyl oxygens
  \end{itemize}

  The diffusion coefficient of simple alcohols increases as the length of 
  the alkane chain increases.
  \begin{itemize}
	\item The dwell times increase as the oily tails become more
	entrapped in monomer tails.
  \end{itemize}

@@

  \subsubsection*{Transport of Acetone}

@@

  \subsubsection*{Transport of Acetic Acid}

@@

  \subsubsection*{Transport of Ions} % probably just sodium

>>>>

  \subsection*{Governing Mechanisms}\label{section:mechanism_overview}

@@

  % BJC: would it be better to report as a fraction of water MSD?
  % BJC: need MSDs of 5 wt % systems here too. Can narrow to study of 10 wt % systems after
  \noindent We calculated the time-averaged MSD of each solute in the set over the
  course of 1 $\mu$s MD simulations. 
  \begin{itemize}
    \item Because the MSDs are non-linear and because of the ageing phenomenon, we
    did not attempt to calculate a diffusion constant as one might for a Brownian
    particle with a linear MSD.
	\item Instead, the values plotted in Figure~\ref{fig:all_msds} represent the
	average MSD of each solute after a 400 ns time lag.
  \end{itemize}

%  \subsubsection*{The Influence of Water Content on Macroscopic Diffusion Coefficients}
%
%  Solutes in systems with lower water content exhibit lower diffusion coefficients.
%  \begin{itemize}
%	\item Pores are more crowded when there is less water (show RDFs of each)
%	\item Not a linear function of pore size - radius increase by x, D increases by y
%	\item Larger influence on bigger molecules
%  \end{itemize}

@@

  \noindent The MSDs in Figure~\ref{fig:all_msds} are a strong function of two solute 
  trapping mechanisms. % by which solutes become trapped.
  \begin{itemize}
  	\item Solutes that are hydrogen bond donors can be stabilized through hydrogen bonds
  	with one of the five oxygen atoms attached to each monomer head group. 
  	\item In a separate interaction, solutes can become kinetically trapped between 
  	monomer head groups. These interactions likely lead to the observed anti-correlated
  	hopping	behavior.
  	\item Generally, both mechanisms affect each solute to varying degrees.
  \end{itemize}

@@

  %BJC: This will need updating once all the rest of outline is written.
  \noindent The degree to which solutes are influenced by each entrapment mechanism
  is a complex function of a solute's size, shape, and polarity.
  \begin{itemize}
    \item In general, solutes can move fastest in the pore center, where
    there is comparatively little resistance to diffusion.
	\item The 5 fastest solutes in our study have a low molecular weight and
	spend a significant amount of time in the pore center. They are only slowed
	by hydrogen bonds with monomer carboxylate groups.
	\item Bulky solutes with many hydrogen bond donating groups, like glycerol,
	spend most of their time in the pore center, but their large size combined
	with a higher solute-head group hydrogen bond frequency, makes their dynamics slow. 
    \item Solutes with high hydrophobic character tend to partition into the 
    head group region where entrapment occurs.
    \item We observe low MW solutes with lower-than-expected MSDs because they
    spend more time trapped between monomer head groups due to low water
    solubility.
    \item Small, planar molecules like acetone exhibit some of the slowest MSDs.
    Their flat geometry and small size makes it easy for them to get lodged deep
    between head groups.
  	\item Overall solutes exhibit some degree of trapping, by one or a combination of the above
  	mechanisms, with anticorrelated hops between each period of immobility due to 
  	obstructions.
  \end{itemize}

@@

  \subsection*{Transport of Water}

  Water molecules also exhibit hop diffusion.

  The overwhelming number of water molecules reduces

@@

  \subsection*{Transport of Simple Alcohols}

  The MSD of methanol, ethanol, propanol and butanol descends in order of 
  their molecular weight, however, methanol travels faster than expected.  %BJC: find approximate relationship between MW and mobility
  \begin{itemize}  
    \item The radial distribution as a function of distance from the pore center
    for each alcohol is plotted in Figure~\ref{fig:simple_alcohol_rdf}.
    \item On average, the density of methanol in the pore center is only slightly
    less than the density near the head groups.
    \item All other alcohol molecules are concentrated in the head group region.
  \end{itemize}

  All simple alcohols participate in a similar number of hydrogen bonding interactions
  with the monomer head groups , but with varying preference towards hydrogen bonds with
  the monomer carboxylate oxygen atoms (See Figure~\ref{fig:simple_alcohol_hbonds}).
  \begin{itemize}
  	\item If all 5 hydrogen bonding acceptor sites on the monomer head groups were equal,
  	we would expect the ratio of the number of hydrogen bonds between solutes and the two 
  	carboxylate oxygen atoms to the number of hydrogen bonds between solutes and the three
  	ether groups to be 2/3. 
  	\item Clearly there is a preference towards hydrogen bonding with the carboxylate 
  	oxygen atoms for all solutes.
  	\item This is largely due to the more highly crowded environment surrounding the ether
  	oxygen atoms.
  	\item Butanol shows the largest preference towards hydrogen bonds with carboxylate 
  	head groups.
  	\item The radial distribution function of atoms located at opposite ends of butanol
  	shows that, on average, oxygen atoms are situated 0.25 nm closer to the pore centers
  	than the distal carbon.
  	\item This suggests that alcohols tend to orient themselves like the liquid crystal 
  	monomers, with hydrophilic components point towards the pore centers.
  \end{itemize}

  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{simple_alcohol_rdf.pdf}
  \caption{}\label{fig:simple_alcohol_rdf}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{simple_alcohol_hbonds.pdf}
  \caption{}\label{fig:simple_alcohol_hbonds}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\linewidth]{butanol_CO.pdf}  %BJC: can add inset to plot showing 
  \caption{}\label{fig:butanol_CO}
  \end{subfigure}
  \caption{(a) The radial distribution functions of each simple alcohol shows a maximum close
  to the highest density of monomer head groups (dashed line, normalized for easier visual
  comparison). Methanol spends the largest proportion of time, relative to the other alcohols,
  near the pore center, which may help explain its fast dynamics. (b) Despite relatively little
  difference in the total number of hydrogen bond occurences, a given alcohol's preference
  towards hydrogen bonds with the carboxylate groups increases with molecule size. (c) The average
  location of butanol's oxygen atom is significantly closer to the pore center than its most distal
  carbon atom, suggesting that the molecule is oriented with hydrophobic tails pointing away from
  the pore center.}\label{fig:simple_alcohols}
  \end{figure}

  \subsection*{Transport of Diols and Triols}

@@

  \subsection*{Transport of Sugars}

  \subsection*{Transport of Ketone-like Solutes}

@@

  \subsection*{Transport of Acetic Acid}

@@

  \subsection*{Transport of Ions} % probably just sodium
